Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
simplified phrasing

\par The academic workshop SemStats series use dokieli in its Website templates, including the call for contributions. CEUR-WS.org, an ``Online Proceedings for Scientific Conferences and Workshops'' offers the tooling ceur-make to help organisers generate proceedings using dokieli’s HTML+RDFa template.
                                    We list a community (of academics) who self-publish their articles and thesis using dokieli with different stylesheets and derived scripts under its examples in the wild. The conference series: WWW e.g., LDOW, WOW, ISWC, and ESWC propose dokieli as one tooling in which authors can use to for their contributions.

>>>>

\par The academic workshop SemStats series use dokieli in its Website templates, including the call for contributions. CEUR-WS.org, an ``Online Proceedings for Scientific Conferences and Workshops'' offers the ceur-make tool to help organisers generate proceedings using dokieli’s HTML+RDFa template.
                                    We list a community (of academics) who self-publish their articles and thesis using dokieli with different stylesheets and derived scripts under its examples in the wild. The conference series: WWW e.g., LDOW, WOW, ISWC, and ESWC propose dokieli as one tooling in which authors can use to for their contributions.
